%-------------------------
% ATS-Optimized Android Developer Resume
% Compatible with Overleaf (pdflatex)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2}
  \end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------

\begin{center}
  {\Huge \textbf{VEERAMANI A}} \\ \vspace{6pt}
  \small
  Phone: +91-6374432752 \quad $|$ \quad
  Email: \href{mailto:veeramaniamk@gmail.com}{veeramaniamk@gmail.com} \quad $|$ \quad
  Chennai, Tamil Nadu \\ \vspace{3pt}
  LinkedIn: \href{https://linkedin.com/in/veeramaniamk}{linkedin.com/in/veeramaniamk} \quad $|$ \quad
  GitHub: \href{https://github.com/veeramaniamk}{github.com/veeramaniamk}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------

\section{Professional Summary}

Android Developer with 2+ years of experience building scalable, high-performance mobile applications using Kotlin and Java. Proficient in Android SDK, Jetpack Compose, MVVM and Clean Architecture, REST API integration with Retrofit and OkHttp, and dependency injection with Dagger Hilt. Experienced in Firebase Cloud Messaging, Razorpay payment integration, and delivering production-ready applications. Passionate about writing maintainable, testable code and creating intuitive user experiences.

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}

\begin{itemize}[leftmargin=0in, label={}, itemsep=2pt]
  \item \textbf{Programming Languages:} Kotlin, Java
  \item \textbf{Android Development:} Android SDK, Jetpack Compose, XML UI, MVVM Architecture, Clean Architecture, Jetpack Libraries
  \item \textbf{Jetpack Components:} ViewModel, LiveData, StateFlow, Room Database, Navigation Component, WorkManager
  \item \textbf{Networking:} Retrofit, OkHttp, REST API Integration, JSON Parsing
  \item \textbf{Dependency Injection:} Hilt, Dagger
  \item \textbf{Database:} Room Database, SQLite, SharedPreferences
  \item \textbf{Tools \& Platforms:} Android Studio, Git, GitHub, Firebase Cloud Messaging (FCM), Razorpay
  \item \textbf{Testing:} JUnit, Espresso (basic)
\end{itemize}

%-----------WORK EXPERIENCE-----------

\section{Work Experience}

\resumeSubHeadingListStart

  \resumeSubheading
    {Saveetha School of Engineering}{Feb 2024 -- Present}
    {Full Stack Android Developer}{Chennai, Tamil Nadu}

  \resumeItemListStart
    \resumeItem{Designed and developed Android applications using \textbf{Kotlin} and \textbf{Java}, following \textbf{MVVM} and \textbf{Clean Architecture} patterns for scalable, maintainable codebases.}
    \resumeItem{Integrated \textbf{Firebase Cloud Messaging (FCM)} for real-time push notifications, improving user engagement.}
    \resumeItem{Built \textbf{REST API} integrations using \textbf{Retrofit} and \textbf{OkHttp} for efficient mobile--backend data communication.}
    \resumeItem{Implemented \textbf{Dagger Hilt} for dependency injection, improving modularity and unit testability across modules.}
    \resumeItem{Developed UI screens using \textbf{Jetpack Compose} and \textbf{XML layouts}, ensuring responsive and accessible interfaces.}
    \resumeItem{Participated in code reviews and contributed to improving team coding standards and best practices.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}

\resumeSubHeadingListStart

  \resumeProjectHeading
    {Spare Finds -- E-Commerce Android Application}{}
  \\\vspace{2pt}
  \textit{\small Tech Stack: Kotlin, MVVM, Retrofit, Firebase, Razorpay, Room DB}

  \resumeItemListStart
    \resumeItem{Developed a full-featured Android e-commerce app for buying and selling \textbf{two-wheeler spare parts}, covering the full flow from catalog to checkout.}
    \resumeItem{Integrated \textbf{Razorpay payment gateway} for secure online transactions with real-time payment status updates.}
    \resumeItem{Implemented \textbf{Firebase Push Notifications} to alert users about order updates, promotions, and delivery status.}
    \resumeItem{Built product catalog, cart management, order processing, and secure \textbf{user authentication} modules.}
    \resumeItem{Optimized data loading and UI responsiveness through efficient \textbf{RecyclerView} usage and pagination.}
  \resumeItemListEnd

  \vspace{6pt}

  \resumeProjectHeading
    {Simats360 -- Employee Management Android Application}{}
  \\\vspace{2pt}
  \textit{\small Tech Stack: Kotlin, Jetpack Compose, MVVM, Dagger Hilt, Retrofit}

  \resumeItemListStart
    \resumeItem{Developed a comprehensive employee management app for attendance tracking, leave requests, and salary details.}
    \resumeItem{Built all UI screens using \textbf{Jetpack Compose} with smooth animations, Material Design components, and responsive layouts.}
    \resumeItem{Implemented \textbf{MVVM architecture} with \textbf{ViewModel} and \textbf{StateFlow/LiveData} for clean separation of concerns and lifecycle awareness.}
    \resumeItem{Used \textbf{Dagger Hilt} for dependency injection, improving testability and decoupling of app components.}
    \resumeItem{Designed dashboards, employee profiles, and reporting screens to streamline \textbf{HR workflow management}.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------

\section{Certifications}

\begin{itemize}[leftmargin=0in, label={}, itemsep=3pt]
  \item \textbf{Java Full Stack Development} \hfill Accord Info Matrix Technologies Pvt Ltd, Chennai
\end{itemize}

%-----------EDUCATION-----------

\section{Education}

\resumeSubHeadingListStart

  \resumeSubheading
    {MRK College of Arts and Science}{2022}
    {Bachelor of Science in Computer Science}{Thiruvalluvar University, Vellore}

\resumeSubHeadingListEnd

\end{document}