%-------------------------
% ATS Friendly Backend Developer Resume — A. Veeramani
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\newcommand{\resumeItem}[1]{\item {#1}}

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{#3} & \textit{#4} \\
\end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------

\begin{document}

%----------HEADING----------

\begin{center}
\textbf{\Huge VEERAMANI A} \\[5pt]
\small
\faPhone\ \href{tel:+916374432752}{+91-6374432752} \quad $|$ \quad
\faEnvelope\ \href{mailto:veeramaniamk@gmail.com}{veeramaniamk@gmail.com} \quad $|$ \quad
\faGithub\ \href{https://github.com/veeramaniamk}{github.com/veeramaniamk} \\[3pt]
\vspace{4pt}
\faLinkedin\ \href{https://linkedin.com/in/veeramaniamk}{linkedin.com/in/veeramaniamk} \quad $|$ \quad
\faMapMarker*\ Chennai, India
\end{center}
%-----------PROFESSIONAL SUMMARY-----------

\section{Professional Summary}

Backend Developer with 2+ years of experience building production-grade Java and Spring Boot applications across e-commerce and enterprise HR domains. Proven ability to design secure RESTful APIs, architect relational database schemas, and integrate third-party services including payment gateways and push notification systems. Delivers clean, modular code with a focus on performance, security, and maintainable architecture.

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}

\textbf{Languages:} Java, MySQL \\
\textbf{Frameworks \& Libraries:} Spring Boot, Spring MVC, Spring Security, Spring Data JPA, Hibernate, Maven \\
\textbf{API Development:} RESTful API Design, JWT Authentication, OAuth 2.0, Swagger / OpenAPI \\
\textbf{Databases:} MySQL, Schema Design, Query Optimization, Indexing \\
\textbf{Integrations:} Razorpay Payment Gateway, Firebase Cloud Messaging (FCM) \\
\textbf{Testing \& Quality:} JUnit, Postman, API Testing \\
\textbf{Tools \& Platforms:} Git, GitHub, IntelliJ IDEA, Microservices Architecture \\

%-----------WORK EXPERIENCE-----------

\section{Work Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Simats Engineering}{Feb 2024 -- Present}
{Backend Developer}{Chennai, India}

\resumeItemListStart

\resumeItem{Architected and delivered scalable backend services using \textbf{Java Spring Boot}, applying modular design and separation-of-concerns principles across multiple production applications.}

\resumeItem{Designed and exposed \textbf{30+ RESTful APIs} consumed by web and Android clients, covering core business flows including authentication, data management, and transactional operations.}

\resumeItem{Implemented \textbf{JWT-based authentication and role-based access control (RBAC)}, securing API endpoints across multiple user roles and preventing unauthorized access to backend services.}

\resumeItem{Engineered \textbf{MySQL database schemas} from scratch — including entity relationships, indexing strategies, and query optimization — resulting in consistent sub-300ms API response times.}

\resumeItem{Integrated \textbf{third-party services} including payment gateways and push notification systems, handling server-side validation, signature verification, and event-driven processing.}

\resumeItem{Collaborated closely with frontend and mobile development teams to define API contracts, resolve integration issues, and ship end-to-end features on schedule.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}

\resumeSubHeadingListStart

\resumeSubheading
{Spare Finds — E-Commerce Platform (Backend)}{}{}{}

\vspace{-18pt}

\textit{Tech Stack: Java, Spring Boot, Spring Security, MySQL, Razorpay, Firebase FCM, JWT, REST APIs}

\resumeItemListStart

\resumeItem{Built the complete backend for a two-wheeler spare parts marketplace, delivering \textbf{RESTful APIs} for product catalogue, cart management, order lifecycle, and user authentication from initial design to production deployment.}

\resumeItem{Integrated \textbf{Razorpay Payment Gateway} with server-side \textbf{HMAC-SHA256 signature verification}, ensuring tamper-proof payment validation and full transaction integrity across all order flows.}

\resumeItem{Designed a normalized \textbf{MySQL schema} supporting product inventory, multi-status order tracking, and user data — optimized with indexed foreign keys and efficient JOIN queries to handle concurrent transactions.}

\resumeItem{Developed an \textbf{event-driven Firebase Cloud Messaging (FCM)} notification engine that triggers real-time push updates to users on order confirmation, payment status, and promotional events.}

\resumeItem{Enforced \textbf{JWT-based API security} across all endpoints with stateless session management, token expiry handling, and protected routes mapped to user roles.}

\resumeItemListEnd

\vspace{6pt}

\resumeSubheading
{Simats360 — Enterprise Employee Management System (Backend)}{}{}{}

\vspace{-18pt}

\textit{Tech Stack: Java, Spring Boot, Spring Security, MySQL, JWT, REST APIs}

\resumeItemListStart

\resumeItem{Engineered backend services for a company-wide HR platform managing \textbf{attendance tracking, leave workflows, and payroll processing} for internal operations at Simats Engineering.}

\resumeItem{Built \textbf{20+ RESTful APIs} covering employee records, leave approval chains, salary computation, and management reporting — integrating seamlessly with web and mobile frontends.}

\resumeItem{Implemented \textbf{JWT security with RBAC}, defining distinct access levels for Admin, HR, and Employee roles, ensuring each user interacts only with permitted data and operations.}

\resumeItem{Designed \textbf{MySQL schemas} for attendance logs, payroll records, and leave history — including data integrity constraints and optimized queries that reduced report generation time significantly.}

\resumeItem{Applied rigorous \textbf{server-side validation and business logic} across all modules — leave eligibility rules, payroll computation logic, and audit trail maintenance — ensuring accurate and reliable HR workflows.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{MRK College of Arts and Science}{2022}
{Bachelor of Science in Computer Science}{Thiruvalluvar University, Vellore}

\resumeSubHeadingListEnd

%-----------CERTIFICATION-----------

\section{Certifications}

\begin{itemize}[leftmargin=0.15in]
\item \textbf{Java Full Stack Development} — Accord Info Matrix Technologies Pvt Ltd, Chennai
\end{itemize}

\end{document}